Mapping Microblog Posts to Encyclopedia Articles

### 2011-03-14 lids/twittersearchwrap/paper/paper.tex
updated table 2

%\usepackage{fullpage}
\usepackage{setspace}
\usepackage{url}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{latexsym}

@@

\begin{table}[ht]
\centering
\small
\begin{tabular}{l|l|l|l}
Hashtag & Extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
\hline
\#tilltheworldends & false & Britney Spears & .9583 \\
& &  iTunes & .6875 \\
& &  itunes & .625 \\ 
\hline
\#nowplaying & false & iTunes & .5208 \\
& & Michael Jackson & .333 \\
& & Lady Gaga & .333 \\
\hline
\#nowplaying & true & YouTube & .8235 \\
& & Hip Hop Music & .6471 \\
& & The Notorious B.I.G. & .5883 \\
\hline
\#np & false & Chris Brown\_(entertainer) & .5 \\
& & Usher & .3125 \\
& & Lil Wayne & .2917 \\
\hline
\#np & true & Chris Brown\_(entertainer) & .5 \\
& & YouTube & .375 \\
& & Ne-Yo & .315 \\
\hline
\#thataintwinning & false & Mozilla Firefox & .2291 \\
& & Twitter & .2291 \\
& & twitter & .1667 \\
\hline
\#thataintwinning & true & twitter & .5208 \\
& & Twitter & .5 \\
& & Two and a half men & .125 \\
\hline
\#blackpeoplemovies & false & Devil & .4791 \\
& & Tyler Perry & .2708 \\
& & Harry Potter & .2292 \\
\hline
\#blackpeoplemovies & true & Amazon.com & 1 \\
& & YouTube & 1 \\
& & amazon.com & 1
\end{tabular}
\label{tbl:entities}
\caption{Most frequent entities and their single term stabilities}
\end{table}

>>>>

%\usepackage{fullpage}
\usepackage{setspace}
\usepackage{url}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{amsmath}
\usepackage{latexsym}
\usepackage{multirow}

@@

\begin{table}[ht]
\centering
\small
\begin{tabular}{l|l|l|l|l}
Hashtag & Definition on tagdef.com & Extern & $E$ & $sts$ \\%& $E_2$ & $sts(E_2)$ & $E_3$ & $sts(E_3)$ \\
\hline
\#tilltheworldends & - & false & Britney Spears & .9583 \\
& & &  iTunes & .6875 \\
& & &  itunes & .625 \\ 
\hline
\#nowplaying & What people on Twitter & false & iTunes & .5208 \\
             & are currently listening & & Michael Jackson & .333 \\
             & to. & & Lady Gaga & .333 \\
\hline
\#nowplaying & same & true & YouTube & .8235 \\
             &  &  & Hip Hop Music & .6471 \\
             &  &  & The Notorious B.I.G. & .5883 \\
\hline
\#np         & Now playing = \#NP & false & Chris Brown\_(entertainer) & .5 \\
& & & Usher & .3125 \\
& & & Lil Wayne & .2917 \\
\hline
\#np & same & true & Chris Brown\_(entertainer) & .5 \\
& & & YouTube & .375 \\
& & & Ne-Yo & .315 \\
\hline
\#thataintwinning & -& false & Mozilla Firefox & .2291 \\
& & & Twitter & .2291 \\
& & & twitter & .1667 \\
\hline
\#thataintwinning & - & true & twitter & .5208 \\
& & & Twitter & .5 \\
& & & Two and a half men & .125 \\
\hline
\#blackpeoplemovies & - & false & Devil & .4791 \\
& & & Tyler Perry & .2708 \\
& & & Harry Potter & .2292 \\
\hline
\#blackpeoplemovies & - & true & Amazon.com & 1 \\
& & & YouTube & 1 \\
& & & amazon.com & 1
\end{tabular}
\label{tbl:entities}
\caption{Most frequent entities and their single term stabilities}
\end{table}
